---
title: "HW5"
author: "Orlando Malanco"
date: "10/26/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r}

library(ggplot2)
data("diamonds")
```


#1a
#This is a histogram of carat and it has 150 bins.this shows the frequency at 
# which the diamonds fall into certain weight.
```{r}
ggplot(diamonds, aes(x = carat)) + geom_histogram(bins = 150) + 
  labs(title = "Number of diamonds within certain carat ranges") 
```

#1b
#this graph plots the price in terms of carat. It color codes them by clarity
# so you can see a vague difference in prices of diamonds due to clarity.
```{r}
ggplot(diamonds, aes(x=carat, y=price, color=clarity)) + geom_point() + 
  labs(title = "price variation in terms of carat and clarity ")
```

#1c
# This graph shows a change in price given weight and distinguishes each point
#by color coding it between clarities. this allows you to compaare prices between 
# cuts as well as see a general line of where the price is for certain clarity
```{r}
ggplot(diamonds, aes(x=carat, y=price, color=clarity)) + geom_point() + 
  geom_smooth(se=FALSE) + labs(title = "Price in Relation to Carat and Clarity")
```


#1d
#This shows the price in terms of weight within a given clarity
```{r}
ggplot(diamonds, aes(x=carat, y=price, color=clarity)) + geom_point() + 
  facet_wrap(clarity ~.) + labs(title = "price in relation to weight given 
                                  clarity")

```


#1e
# the violin graph is better for visualisation because it shows the density 
#of the weights within a cut
```{r}
ggplot(diamonds, aes(x = carat, y = cut)) + geom_violin() + 
  labs(title = "density of types of cut given weight")

ggplot(diamonds, aes(x = carat, y = cut)) + 
  geom_boxplot(outlier.colour="red") + 
  labs(title = "variation of wight within a cut")

ggplot(diamonds, aes(x = carat, y = cut)) +
  geom_jitter() + labs(title = "weight of diamond within certain cuts")

  ggplot(diamonds, aes(x = carat, y = cut)) + geom_point() + 
  labs(title = "diamond cuts and their weights")


```

#2a
# The forst graph is better at comparing the cuts within a given clarity and can
# used to compare which is clarity is better for certain cuts but the graph that
# splits up the cuts can be used to compare the clarities within a given cut
```{r}
ggplot(diamonds, aes(x = clarity, fill = cut)) + 
  geom_bar(position = position_dodge())
ggplot(diamonds, aes(x = clarity, fill = cut)) + 
  geom_bar(position = position_dodge()) + facet_grid(cut~.) 

```
#2b

```{r}
ggplot(diamonds, aes(x = carat, y = price, col = clarity)) + 
  geom_smooth(se = FALSE, method = lm)
```
#2c

```{r}
ggplot(diamonds, aes(x = clarity, y = price, col = cut)) + 
  geom_boxplot()
```


#2d

```{r}
ggplot(diamonds, aes(x = carat, y = price, col = cut)) + 
  geom_boxplot()
```